Convolutional Neural Networks and Volcano Plots: Screening and Prediction of Two-Dimensional Single-Atom Catalysts for CO\textsubscript{2} Reduction Reactions

### 2024-01-15 paper/arxiv/main_4.1_cnn_for_eads.tex
revise figure captions

% Figure 2: CNN for eDOS
\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{main_fig2_cnn.png}
    \caption{\textbf{CNN for Electronic Density of States.}
    \textbf{a}. Kendall rank correlation map illustrating the correlation
    between adsorption energy and some electronic and elementary descriptors.
    Definitions of the notations are provided in
    Supplementary \cref{supp_table15:descriptor_notations}.
    \textbf{b}-\textbf{c}. Architectural of (\textbf{b})the root and
    (\textbf{c})each branch of the CNN model.
    The architecture remains consistent across individual branches.
    \textbf{d}-\textbf{m}. Parity plots demonstrating the performance of the
    CNN model across nine adsorbates:
    (\textbf{d}) all adsorbates, (\textbf{e}) CO\textsubscript{2}, (\textbf{f})COOH,
    (\textbf{g})CO, (\textbf{h})CHO, (\textbf{i}) CH\textsubscript{2}O,
    (\textbf{j}) OCH\textsubscript{3}, (\textbf{k})O, (\textbf{l})OH, and (\textbf{m})H.
    The augmentation data are not displayed in the plots nor included in MAE evaluations.
    Kernel density estimate results are shown along the top and right sides of the main plot,
    representing DFT calculations and CNN model prediction distributions, respectively.}
    \label{main_fig2:cnn_for_eads}
\end{figure}

>>>>

% Figure 2: CNN for eDOS
\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{main_fig2_cnn.png}
    \caption{\textbf{CNN for Electronic Density of States.}
    \textbf{a}. Kendall rank correlation map illustrating the correlation
    between adsorption energy and other electronic and elementary descriptors.
    Definitions of the notations are provided in
    Supplementary \cref{supp_table15:descriptor_notations}.
    \textbf{b}-\textbf{c}. Architectural of (\textbf{b}) the root and
    (\textbf{c}) each branch of the CNN model.
    The architecture stays consistent across individual branches.
    \textbf{d}-\textbf{m}. Parity plots demonstrating the performance of the
    CNN model across nine adsorbates:
    (\textbf{d}) all adsorbates, (\textbf{e}) CO\textsubscript{2}, (\textbf{f}) COOH,
    (\textbf{g}) CO, (\textbf{h}) CHO, (\textbf{i}) CH\textsubscript{2}O,
    (\textbf{j}) OCH\textsubscript{3}, (\textbf{k}) O, (\textbf{l}) OH, and (\textbf{m}) H.
    The augmentation data are not displayed in these plots, nor included in MAE evaluations.
    Kernel density estimate results are shown along the top and right sides of the main plot,
    representing DFT calculations and CNN model prediction distributions, respectively.}
    \label{main_fig2:cnn_for_eads}
\end{figure}

### 2024-01-15 paper/arxiv/main_4.3_validation.tex
revise figure captions

% Figure 4: Validation of CNN Predictions
\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{main_fig4_validation.png}
    \caption{\textbf{Validation of CNN Predictions.}
    \textbf{a}-\textbf{c}, The occlusion experiment results for (\textbf{a})Cr
    $d_{x^2-y^2}$ orbital of Cr@g-C\textsubscript{3}N\textsubscript{4},
    (\textbf{b})Co $d_{xy}$ orbital of Co@g-C\textsubscript{3}N\textsubscript{4} and
    (\textbf{c})Cu $d_{xy}$ orbital of Cu@g-C\textsubscript{3}N\textsubscript{4}.
    Occlusion experiments were conducted on the initial states of CO adsorption process.
    \textbf{d}-\textbf{f}, Real-space wavefunction visualization for (\textbf{d})Cr
    $d_{x^2-y^2}$ orbital of Cr@g-C\textsubscript{3}N\textsubscript{4}, (\textbf{e})Co
    $d_{xy}$ orbital of Co@g-C\textsubscript{3}N\textsubscript{4} and (\textbf{f})Cu
    $d_{xy}$ orbital of Cu@g-C\textsubscript{3}N\textsubscript{4}.
    Wavefunction visualizations were performed on the final states of CO adsorption process.
    The yellow and aqua colors represent areas of positive and negative
    Kohn-Sham orbital coefficients, respectively.
    \textbf{g}-\textbf{j}, Occlusion experiment results for (\textbf{g})$d_{xy}$ orbital
    and (\textbf{h})$d_{xz}$ orbital for Co of Co@g-C\textsubscript{3}N\textsubscript{4}.
    COHP analysis for (\textbf{i})$d_{xy}$ orbital and (\textbf{j})$d_{xz}$ orbital for
     Co of Co@g-C\textsubscript{3}N\textsubscript{4}, performed between Co and
     all adsorbate atoms in the final states of CO adsorption process.}
    \label{main_fig4:validation}
\end{figure}

>>>>

% Figure 4: Validation of CNN Predictions
\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{main_fig4_validation.png}
    \caption{\textbf{Validation of CNN Predictions.}
    \textbf{a}-\textbf{c}, The eDOS occlusion experiment results for
    (\textbf{a}) Cr of Cr@g-C\textsubscript{3}N\textsubscript{4},
    (\textbf{b}) Co of Co@g-C\textsubscript{3}N\textsubscript{4} and
    (\textbf{c}) Cu of Cu@g-C\textsubscript{3}N\textsubscript{4}.
    eDOS occlusion experiments were conducted on the initial states of CO adsorption process.
    \textbf{d}-\textbf{f}, Real-space wavefunction visualization for
    (\textbf{d}) Cr $d_{x^2-y^2}$ orbital of Cr@g-C\textsubscript{3}N\textsubscript{4},
    (\textbf{e}) Co $d_{xy}$ orbital of Co@g-C\textsubscript{3}N\textsubscript{4} and
    (\textbf{f}) Cu $d_{xy}$ orbital of Cu@g-C\textsubscript{3}N\textsubscript{4}.
    Wavefunction visualizations were performed on the final states of CO adsorption process.
    The yellow and aqua colors represent areas of positive and negative
    Kohn-Sham orbital coefficients, respectively.
    \textbf{g}-\textbf{j}, Occlusion experiment results for (\textbf{g}) $d_{xy}$ orbital
    and (\textbf{h}) $d_{xz}$ orbital for Co of Co@g-C\textsubscript{3}N\textsubscript{4}.
    COHP analysis for (\textbf{i}) $d_{xy}$ orbital and (\textbf{j}) $d_{xz}$ orbital for
    Co of Co@g-C\textsubscript{3}N\textsubscript{4}, performed between Co and
    all adsorbate atoms in the final states of CO adsorption process.}
    \label{main_fig4:validation}
\end{figure}

### 2024-01-15 paper/arxiv/main_4.4_shifting_exp.tex
revise figure captions

\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{main_fig5_shifting.png}
    \caption{\textbf{Shifting Experiments.}
    Impact of orbitalwise eDOS shifting on CO adsorption energy, as predicted by the CNN model,
    for single metal atom catalysts supported on g-C\textsubscript{3}N\textsubscript{4}.
    The disturbances caused by shifting of (a)entire $d$, (b)$d_{xy}$, (c)$d_{yz}$,
    (d)$d_{z^2}$, (e)$d_{xz}$ and (f)$d_{x^2-y^2}$ orbitals are illustrated.
    The shifting step size corresponds to the energy resolution of the eDOS, which is 0.005 eV in this study.
    A positive eDOS shift indicates a shift towards higher energy levels, and vice versa.}
    \label{main_fig5:shifting}
\end{figure}

>>>>

% Figure 5: Shifting Experiments
\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{main_fig5_shifting.png}
    \caption{\textbf{Shifting Experiments.}
    Impact of orbitalwise eDOS shifting on CO adsorption energy, as predicted by the CNN model,
    for single metal atom catalysts supported on g-C\textsubscript{3}N\textsubscript{4}.
    The disturbances caused by shifting of (\textbf{a}) entire $d$, (\textbf{b}) $d_{xy}$,
    (\textbf{c}) $d_{yz}$, (\textbf{d}) $d_{z^2}$, (\textbf{e}) $d_{xz}$ and
    (\textbf{f}) $d_{x^2-y^2}$ orbitals are illustrated.
    The shifting step size corresponds to the energy resolution of the eDOS,
    and is 0.005 eV in this study.
    A positive eDOS shift indicates a shift towards higher energy levels, and vice versa.}
    \label{main_fig5:shifting}
\end{figure}
